XRONOS: An Open Data Infrastructure for Archaeological Chronology

### 2024-12-05 paper.qmd
Use title case
Per JCAA guidelines
Save figures in figures/
Generate double blind version
Add Zenodo DOI

title: "XRONOS: an open data infrastructure for archaeological chronology"

@@

      formatting: review

@@

@@

# State of the art

@@

# Funding statement

@@

# Data accessibility statement

The data and R code used to produce our analysis of the state of the art in radiocarbonc compilation, including all the figures presented here, can be accessed via Zenodo at (<!-- TODO: add link -->*link omitted for blind review, included in submission materials*)

>>>>

title: "XRONOS: An Open Data Infrastructure for Archaeological Chronology"

@@

      formatting: doubleblind

@@

knitr:
  opts_chunk:
    fig.path: figures/

@@

# State of the Art

@@

# Funding Statement

@@

# Data Accessibility Statement

The data and R code used to produce our analysis of the state of the art in radiocarbon compilation, including all the figures presented here, can be accessed via Zenodo at <https://doi.org/10.5281/zenodo.14282598>.

### 2024-12-05 paper.tex
Generate double blind version
Add Zenodo DOI

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number,
  review]{elsarticle}

@@

The data and R code used to produce our analysis of the state of the art
in radiocarbonc compilation, including all the figures presented here,
can be accessed via Zenodo at (\emph{link omitted for blind review,
included in submission materials})

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number,
  doubleblind]{elsarticle}

@@

The data and R code used to produce our analysis of the state of the art
in radiocarbon compilation, including all the figures presented here,
can be accessed via Zenodo at
\url{https://doi.org/10.5281/zenodo.14282598}.
